\documentclass[11pt,a4paper]{article}

% ===================== PACKAGES =====================
\usepackage[margin=1.5cm]{geometry}
\usepackage{fontspec}
\usepackage{unicode-math}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{array}
\usepackage{titlesec}
\usepackage{ragged2e}
\usepackage{setspace}
\usepackage{microtype}
\usepackage{fontawesome5}

% ===================== FONTS =====================
\setmainfont{TeX Gyre Termes}
\setsansfont{TeX Gyre Heros}
\setmonofont{TeX Gyre Cursor}
\setmathfont{TeX Gyre Termes Math}

% ===================== COLORS =====================
\definecolor{Accent}{HTML}{1F4E79}
\definecolor{SoftGray}{HTML}{555555}
\definecolor{NameGray}{HTML}{666666}

% ===================== PDF / LINKS =====================
\hypersetup{
  colorlinks=true,
  linkcolor=Accent,
  urlcolor=Accent,
  citecolor=Accent,
  pdftitle={Md Imam Ahasan - Academic CV},
  pdfauthor={Md Imam Ahasan}
}
\urlstyle{same}

% ===================== GLOBAL SPACING =====================
\setlength{\parindent}{0pt}
\setlength{\parskip}{1.5pt}
\renewcommand{\baselinestretch}{1.02}
\raggedbottom
\emergencystretch=3em

% ===================== SECTION STYLING =====================
\titleformat{\section}
  {\large\bfseries\sffamily\color{Accent}}
  {}{0pt}{}
  [\vspace{1pt}\titlerule]
\titlespacing*{\section}{0pt}{7pt}{3pt}

% ===================== LISTS =====================
\setlist[itemize]{
  leftmargin=1.2em,
  itemsep=1pt,
  topsep=0pt,
  parsep=0pt,
  partopsep=0pt
}
\setlist[description]{
  itemsep=4pt,
  topsep=2pt,
  parsep=0pt,
  partopsep=0pt
}

% ===================== CUSTOM COMMANDS =====================
\newcommand{\EntryHeadingTwo}[4]{%
  \textbf{#1}\hfill \textbf{#2}\\
  \textit{#3}\hfill \textit{#4}\\
}

% Contribution note (gray, indented, within a pub item)
\newcommand{\PubNote}[1]{%
  \\[1pt]{\small\color{SoftGray}$\triangleright$\enspace#1}%
}

% Publication subsection heading
\newcommand{\pubsub}[1]{\vspace{4pt}\textbf{#1}\vspace{1pt}}

% ------- Document -------
\begin{document}

% ===================== HEADER =====================
\begin{center}
  {\fontsize{34}{38}\selectfont\sffamily
    \textcolor{NameGray}{Md Imam }\textbf{\textcolor{black}{Ahasan}}
  }\par
  \vspace{2pt}
  {\small\itshape\color{SoftGray}
    Chongqing University, Huxi Campus, Shapingba District, Chongqing 401331, China
  }\par
  \vspace{2pt}
  {\small\sffamily\color{SoftGray}
    \faPhone\ (+86)\,13008309195 \enspace\textbar\enspace
    \faEnvelope\ \href{mailto:emamahasane@gmail.com}{emamahasane@gmail.com} \enspace\textbar\enspace
    \faGithub\ \href{https://github.com/imamahasane}{imamahasane} \enspace\textbar\enspace
    \faLinkedin\ \href{https://www.linkedin.com/in/imamahasane}{imamahasane}
  }\par
\end{center}

% ===================== EDUCATION =====================
\section*{Education}

\EntryHeadingTwo
  {Chongqing University (CQU)}{Chongqing, China}
  {M.Sc.\ in Computer Science}{Sep 2023 -- Jun 2026}
{\small GPA: 83.4\,/\,100\enspace{\color{SoftGray}Top\,1\% of international cohort}}\newline
{\small\textit{Thesis:} ``Research on Low-Dose Computed Tomography Image Reconstruction'' -- Developed DACD and GenDiff, two physics-guided diffusion frameworks for LDCT reconstruction. Supervisor: Dr.\ Guangchao Yang, College of Computer Science, CQU}

\vspace{3pt}

\EntryHeadingTwo
  {Daffodil International University (DIU)}{Dhaka, Bangladesh}
  {B.Sc.\ in Computer Science and Engineering}{Sep 2017 -- Sep 2021}
{\small GPA: 71.5\,/\,100}\newline
{\small\textit{Thesis:} ``Gronthon: Bangla PDF to Text Conversion Application'' -- Developed an end-to-end OCR pipeline for Bengali script digitization. Supervisor: Dr.\ Md Zahid Hasan, Computer Science and Technology, DIU}

% ===================== PUBLICATIONS =====================
\section*{Publications}

{\small\color{SoftGray}\textit{%
  \textbf{(FA)} = First Author.\enspace
  ${}^\dagger$ = Corresponding Author.\enspace
  [C] = Conference Paper.\enspace
  [J] = Journal Article.\enspace
  [R] = Under Review.\enspace
}}

\pubsub{Peer-Reviewed Conference/Journal Papers}

\begin{description}[leftmargin=3.0em, labelwidth=2.6em, labelsep=0.4em,
                    itemsep=5pt, topsep=2pt, parsep=0pt]

\item[{\textbf{[C1]}}] \textbf{(FA)} \textbf{Md Imam Ahasan}, Guangchao Yang$^\dagger$,
  A F M Abdun Noor, S M Hasan Mahmud.
  ``Dose-Aware Cold Diffusion with Physics Consistency for Generalizable Low-Dose CT
  Reconstruction.'' \textit{Intl.\ Joint Conf.\ on Neural Networks (IJCNN 2026).}
  \textbf{[Accepted\,$\cdot$\,CCF-C]}

\item[{\textbf{[C2]}}] A F M Abdun Noor, \textbf{Md Imam Ahasan},
  Mohammad Azam Khan, Guangchao Yang$^\dagger$.
  ``GeGLUNet: Structural Retinal Vessel Segmentation via Attention-Gated GeGLU and
  Contrastive Supervision.'' \textit{Conf.\ on Pattern Recognition and Computer Vision
  (PRCV 2025).}
  \href{https://doi.org/10.1007/978-981-95-5631-1_35}%
       {\small 10.1007/978-981-95-5631-1\_35}.
  \textbf{[Published\,$\cdot$\,CCF-C]}

\item[{\textbf{[C3]}}] Md Mahfuzur Rahman, Pengzhan Zhou$^\dagger$,
  A F M Abdun Noor, \textbf{Md Imam Ahasan}.
  ``MTF-Net: Multi-Modal Temporal Feature Fusion Network for Pedestrian Intention
  Prediction.'' \textit{Intl.\ Conf.\ on Cloud and Network Computing (ICCNC 2026).}
  \textbf{[Accepted\,$\cdot$\,EI]}

\item[{\textbf{[C4]}}] Anum Malik, Mahnoor Buriro, Muhammad Younas Khan,
  \textbf{Md Imam Ahasan}.
  ``MoSSGate: Memory-Modulated State-Space Gating for Skin Lesion Segmentation.''
  \textit{ICCNC 2026.} \textbf{[Accepted\,$\cdot$\,EI]}

\item[{\textbf{[J1]}}] Ahtisham Waheed, Yunfei Yin$^\dagger$,
  A F M Abdun Noor, \textbf{Md Imam Ahasan}.
  ``Direction-Curvature Aware Feature Integration for Robust Lane Detection.''
  \textit{Computers, Materials and Continua (CMC).} \textbf{[Accepted\,$\cdot$\,SCIE]}

\end{description}

\pubsub{Under Review}

\begin{description}[leftmargin=3.0em, labelwidth=2.6em, labelsep=0.4em,
                    itemsep=5pt, topsep=2pt, parsep=0pt]

\item[{\textbf{[R1]}}] \textbf{(FA)} \textbf{Md Imam Ahasan}, Guangchao Yang$^\dagger$,
  A F M Abdun Noor, S M Hasan Mahmud$^\dagger$.
  ``GenDiff: A Dose and Anatomy Aware Diffusion Model with Structural Prior Refinement
  for Low-Dose CT Reconstruction and Generalization.''
  \textit{PeerJ Computer Science.} \textbf{[Under Review\,$\cdot$\,SCIE]}

\item[{\textbf{[R2]}}] Md Mustafizur Rahman, Guangchao Yang,
  A F M Abdun Noor, \textbf{Md Imam Ahasan}, Md Mahfuzur Rahman.
  ``TSCA-Net: Temporal-Spatial Clique Attention for Interpretable Multimodal Pedestrian Trajectory Prediction.''
  \textit{IEEE Intl.\ Conf.\ on Data Mining (ICDM 2026).}
  \textbf{[Under Review\,$\cdot$\,CCF-B]}

\item[{\textbf{[R3]}}] \textbf{(FA)} \textbf{Md Imam Ahasan}, Guangchao Yang$^\dagger$,
  A F M Abdun Noor, Mohammad Azam Khan$^\dagger$.
  ``LightGAN-LD: A Lightweight Generative Adversarial Network for Efficient Low-Dose CT
  Reconstruction with Sinogram Encoding and Edge-Aware Learning.''
  \textit{PeerJ Computer Science.} \textbf{[Under Review\,$\cdot$\,SCIE]}

\item[{\textbf{[R4]}}] \textbf{(FA)} \textbf{Md Imam Ahasan},
  A F M Abdun Noor, Kah Ong Michael Goh$^\dagger$, S M Hasan Mahmud$^\dagger$.
  ``Toward Real-Time LDCT Reconstruction: A Sinogram-Encoded Lightweight GAN with
  Measurement-Domain Noise Suppression.''
  \textit{Computers, Materials and Continua (CMC).} \textbf{[Under Review\,$\cdot$\,SCIE]}

\item[{\textbf{[R5]}}] A F M Abdun Noor, \textbf{Md Imam Ahasan},
  Kah Ong Michael Goh$^\dagger$, S M Hasan Mahmud.
  ``QBiLoF-U-Net: Bi-Context Location-Aware Feature Modeling for Joint Mammographic
  Segmentation and Classification.''
  \textit{Computer Modeling in Engineering and Sciences (CMES).}
  \textbf{[Under Review\,$\cdot$\,SCIE]}

\item[{\textbf{[R6]}}] Md Mahfuzur Rahman, Pengzhan Zhou$^\dagger$,
  A F M Abdun Noor, \textbf{Md Imam Ahasan}.
  ``Adaptive Cross-Modal Fusion with Sparse Attention for Pedestrian Crossing Intention
  Prediction.'' \textit{PeerJ Computer Science.} \textbf{[Under Review\,$\cdot$\,SCIE]}

\end{description}

% ===================== RESEARCH EXPERIENCE =====================
\section*{Research Experience}

\EntryHeadingTwo
  {Graduate Research Assistant -- Computer Vision Lab}{Chongqing University, China}
  {Supervisor: Dr.\ Guangchao Yang, College of Computer Science}{Sep 2023 -- Jun 2026}
\vspace{-8pt}
\begin{itemize}
  \item Designed \textbf{DACD}, a Poisson-thinning cold diffusion model with physics consistency achieving $+$1.20\,dB PSNR over SOTA and 3.3$\times$ faster inference. \textit{[IJCNN 2026, CCF-C - Accepted]}
  \item Extended to \textbf{GenDiff} with dose-anatomy encoding and structural prior refinement for zero-shot generalization across unseen dose levels and anatomical domains. \textit{[PeerJ CS, SCIE - Under Review]}
  \item Developed \textbf{LightGAN-LD} and \textbf{Physics-Conditioned Bayesian Diffusion} model for real-time LDCT reconstruction in collaboration with Dr.\ Mohammad Azam Khan (KAIST). \textit{[BIBM 2026, CCF-B; PeerJ CS, SCIE - Under Review]}
\end{itemize}

\vspace{3pt}

\EntryHeadingTwo
  {Graduate Research Assistant - Data Science Lab}{Daffodil International University, Bangladesh}
  {Supervisor: Dr.\ Md Zahid Hasan, Computer Science and Technology}{Jun 2020 -- Jul 2021}
\vspace{-8pt}
\begin{itemize}
  \item Developed and benchmarked deep learning pipelines for retinal vessel segmentation and skin lesion classification across standard public datasets, building foundational expertise in medical image analysis.
  \item Co-developed \textbf{GeGLUNet}, a retinal vessel segmentation network via attention-gated GeGLU and contrastive supervision. \textit{[PRCV 2025, CCF-C - Published]}
\end{itemize}

% ===================== TEACHING & PROFESSIONAL =====================
\section*{Teaching \& Professional Experience}

\textbf{Lecturer, ICT:}\enspace Anupama Intl.\ School and College \hfill Dhaka, Bangladesh \enspace\textbar\enspace Dec 2021 -- Jun 2022

\vspace{3pt}

\textbf{Senior IT Support Engineer:}\enspace Surma Garments Ltd. \hfill Dhaka, Bangladesh \enspace\textbar\enspace Aug 2022 -- Jun 2023

% ===================== AWARDS =====================
\section*{Awards \& Honors}

\begin{tabularx}{\textwidth}{@{}X r@{}}
  \textbf{CQU Outstanding International Graduates 2026}
    {\;\small\color{SoftGray}Awarded to top\,1\% of international graduates}
    & Jun 2026 \\[2pt]
  \textbf{3\textsuperscript{rd} Prize}, ``China in My Eyes'' Photography Contest
    & Oct 2024 \\[2pt]
  \textbf{Finalist}, Joy Bangla Youth Award
    {\;\small\color{SoftGray}National recognition for social and community impact}
    & Aug 2021 \\[2pt]
  \textbf{Co-Founder}, Shopner Khoje Foundation (\textit{charitable organization})
    & Feb 2017 -- Present \\
\end{tabularx}

% ===================== TECHNICAL SKILLS =====================
\section*{Technical Skills}

\begin{tabularx}{\textwidth}{@{}l X@{}}
  \textbf{Programming}      & Python \\[2pt]
  \textbf{DL Frameworks}    & PyTorch (custom training loops, mixed precision, multi-GPU),
                               MONAI, scikit-learn \\[2pt]
  \textbf{Domain Expertise} & Diffusion Models (cold diffusion, DDPM, score-based),
                               GANs, Inverse Problems, CT\,/\,Sinogram Processing,
                               Physics-Informed Deep Learning, Medical Image Segmentation,
                               LDCT Reconstruction \\[2pt]
  \textbf{Tools}            & Git, Linux, \LaTeX, Weights \& Biases (W\&B) \\
\end{tabularx}

% ===================== ACADEMIC SERVICE =====================
\section*{Academic Service}

\textbf{Peer Reviewer:}\enspace
\textit{Engineering Applications of Artificial Intelligence} (EAAI),
\textit{Systems \& Soft Computing},
\textit{Journal of Agriculture and Food Research},
PRCV {\small\color{SoftGray}\textit{2025}},
IJCNN {\small\color{SoftGray}\textit{2026}}.

\vspace{3pt}

\textbf{Conference Volunteer:}\enspace
2018 ICPC Asia Dhaka Regional Contest;\enspace
6th Intl.\ Conf.\ on Electronic Engineering and Informatics
{\small\color{SoftGray}\textit{2024}};\enspace
IEEE Intl.\ Conf.\ on Electrical Energy Conversion Systems and Control
{\small\color{SoftGray}\textit{2025}}.

% ===================== REFERENCES =====================
\section*{References}

\begin{tabularx}{\textwidth}{@{}X X@{}}
  \begin{minipage}[t]{0.48\textwidth}
    \textbf{Dr.\ Guangchao Yang}\\
    College of Computer Science\\
    Chongqing University, Chongqing, China\\
    \href{mailto:gchao_yang@cqu.edu.cn}{gchao\_yang@cqu.edu.cn}\enspace\textbar\enspace
    +86\,15923504788
  \end{minipage}
  &
  \begin{minipage}[t]{0.48\textwidth}
    \textbf{Dr.\ Mohammad Azam Khan}\\
    Kim Jaechul Graduate School of AI\\
    Korea Advanced Institute of Science and Technology\\
    \href{mailto:azamkhan@kaist.ac.kr}{azamkhan@kaist.ac.kr}
  \end{minipage}
\end{tabularx}

\end{document}